Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-09-06 Manuscript Analyses/manuscript_analysis.Rmd

cog_table <- pl_int %>%
  dplyr::filter(type == "pretest") %>%
  dplyr::select(id, speaker, age, ends_with("_c"), best_win) %>%
  dplyr::select(-c(fluid_cog_c, pic_seq_c)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  group_by(id, speaker) %>% 
  summarize(across(everything(), first)) %>% 
  ungroup() %>% 
  select(-id) %>% 
  tbl_summary(
    by = "speaker",
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

@@

```{r}

@@

compare_table_c <- compare_df %>%
  dplyr::select(id, ends_with("_c"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = win
  ) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

@@

```{r}

compare_table_u <- compare_df %>%
  dplyr::select(id, ends_with("_u"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_u,
    `Inhibitory Control` = flanker_u,
    `Cognitive Flexibility` = card_sort_u,
    `Receptive Vocabulary` = vocab_u,
    `Processing Speed` = pattern_u,
    `Words in Noise Threshold` = win
  ) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

@@

@@

The plot below shows only the significant correlations in the matrix above for AM1.

cor_df %>%
  dplyr::filter(speaker == "AM1") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, pic_seq_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c(my_pal[1], "white", my_pal[15]),
    lab = TRUE,
    p.mat = cor_pmat(.),
    sig.level = 0.05,
    insig = "blank",
    title = "Ataxic", 
    legend.title = "Correlation"
  )

@@

The plot below only shows the significant correlations for PDM10.

```{r}

cor_df %>%
  dplyr::filter(speaker == "PDM10") %>%
  dplyr::select(!c(id, speaker, fluid_cog_c, pic_seq_c, posttest)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  dplyr::rename_all(snakecase::to_title_case) %>%
  cor(use = "pairwise.complete.obs") %>%
  ggcorrplot(
    type = "lower",
    outline.col = "white",
    colors = c(my_pal[1], "white", my_pal[15]),
    lab = TRUE,
    p.mat = cor_pmat(.),
    insig = "blank",
    sig.level = 0.05,
    title = "Parkinson's Disease", 
    legend.title = "Correlation"
  )

>>>>

cog_table <- pl_int %>%
  dplyr::filter(type == "pretest") %>%
  dplyr::select(id, speaker, age, ends_with("_c"), best_win) %>%
  dplyr::select(-c(fluid_cog_c, pic_seq_c)) %>%
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = best_win
  ) %>%
  select(-id) %>% 
  tbl_summary(
    by = "speaker",
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p() %>%
  as_gt()

@@

@@

compare_table_c <- compare_df %>%
  dplyr::select(id, ends_with("_c"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_c,
    `Inhibitory Control` = flanker_c,
    `Cognitive Flexibility` = card_sort_c,
    `Receptive Vocabulary` = vocab_c,
    `Processing Speed` = pattern_c,
    `Words in Noise Threshold` = win
  ) %>%
  dplyr::mutate(group = factor(group, levels = c("young", "old"))) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p()

@@

compare_table_u <- compare_df %>%
  dplyr::select(id, ends_with("_u"), win, group) %>% 
  dplyr::rename(
    `Working Memory` = list_sort_u,
    `Inhibitory Control` = flanker_u,
    `Cognitive Flexibility` = card_sort_u,
    `Receptive Vocabulary` = vocab_u,
    `Processing Speed` = pattern_u,
    `Words in Noise Threshold` = win
  ) %>%
  dplyr::mutate(group = factor(group, levels = c("young", "old"))) %>%
  select(-id) %>% 
  tbl_summary(
    by = group,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    missing = "no",
    digits = list(everything() ~ c(2))
  ) %>% 
  add_p()

@@

```{r, eval = F}

tbl_merge(tbls = list(compare_table_u, compare_table_c),
          tab_spanner = c("***Uncorrected Standardized Scores***", "***Age-Corrected Standardized Scores***")) |>
  as_gt() |>
  gt::gtsave("Tables/compare_table.html")

```{r, echo = F}

rm(young_adult, older_adult, compare_table_c, compare_table_u, compare_df)

@@

@@
